Appendix

### 2021-05-04 paper/preprint/appendix.Rmd
reworking sections to accomodate new bb analyses

```{r}
bin_size=30
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

all_vid_bbs <- all_vid_bbs %>%
  mutate(age_months = age_days/30.4) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=paste0(as.character(round(bin_starts/30,1)), ' m.o.'))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
  filter(num_detect > 100)

@@

>>>>

```{r}
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

all_vid_bbs <- all_vid_bbs %>%
  mutate(age_months = age_days/30.4) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=floor(bin_starts/30.4))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
  filter(num_detect > 100)

@@

```{r}
CV_faces <- all_vid_bbs %>%
  filter(label=='face') %>%
  group_by(age_day_bin,child_id) %>%
  summarize(cv_x_pos = sd(avg_center_x)/mean(avg_center_x)*100, cv_y_pos = sd(avg_center_y)/mean(avg_center_y)*100, num_detect = sum(num_detect), num_vids = n()) %>%
  pivot_longer(cols = c(cv_y_pos, cv_x_pos), values_to = "CV", names_to = "position") %>%
  mutate(position = factor(position, levels = c("cv_x_pos","cv_y_pos"), labels = c("X Position", "Y Position")))

```{r}
ggplot(CV_faces, aes(x=age_day_bin , y = CV, size=num_detect, color=child_id)) +
  geom_point(alpha=.3) + 
  facet_wrap(~position)  +
  geom_smooth(method='lm') +
  scale_color_brewer(palette='Dark2') + 
  ylab('Coefficient of variation for face position') +
  xlab('Age (in months)') +
  guides(size = FALSE)
```
